Behavior Driven Development in Haskell

### 2012-06-01 paper.tex
Update comment

\begin{quote}
    \emph{sol: Can we remove what follows?}

    \emph{kazu: I want to keep them for readability.}

    \emph{sol: For me it really depends on how often we use something.
    If we only use it once or twice, I'd try make it clear from the
    context what is meant.}
\end{quote}

>>>>

\begin{quote}
    \emph TBD: Check, terminology for consistency, and remove
    unnecessary terminology (if any).  This has to be done as one of
    the last steps.
\end{quote}
